\subsection{Intel's Running Average Power Limit (RAPL)}\label[subsec]{subsec:rapl}
This section about RAPL is inspired by Nielsen et al. in \cite{Doom2021}.
RAPL is a tool that allows for measuring and limiting the energy consumption of different power domains in the processor. RAPL is a software based model for estimating energy consumption using hardware performance counters and I/O models through several model-specific registers (MRS) in Intel processors dedicated to RAPL.\cite{Power-Management_Sandy_Bridge,Zhang2021} The accuracy of the energy consumption is high even though it is a software power model\cite{RAPL_ACU1,hackenberg2013}. RAPL has in some works been found to be correlated with the power consumption from the wall with a coefficient of $0.99$ for some work loads,\cite{RAPL_in_action} while other works has found RAPL to have a tendency of under-reporting and found no correlation with a ground truth.\cite{fahad2019comparative} RAPL was introduced with Intel's Sandy Bridge architecture in 2011 and it has since improved with the generations of new chips. In Intel Haswell (2013) the control of the frequencies was improved and along with on-chip voltage regulators, the accuracy of RAPL improved. When Intel Skylake (2015) was released, a new domain was added (PSys) as well as better granularity for the PP0 measurements. Khan et al.\cite{RAPL_in_action} found that RAPL is a viable alternative to manual complex power monitors with a low and negligible performance overhead. \cite{RAPL_in_action}\newline

The different power domains which are supported are shown in \cref{tab:RAPL_Domain}. Although there are some limitations, since not all power domains are supported by each processor model e.g. PP1 is only supported on desktop models.
% \todo[]{Simliar itemize in E3, but in a tabel instead. Consistency is key}
% \begin{itemize}
%     \item CPU package (PKG): Includes the consumption of the entire socket which is all cores and uncore components which are parts that are not in the core, but is closely connected e.g. caches, memory controller, integrated graphics.
%     \item DRAM: Includes the consumption of the RAM which is integrated into the memory controller.  
%     \item Power Plane 0 (PP0): Includes the consumption of all cores. Excluding uncore components.
%     \item Power Plane 1 (PP1): Includes uncore components. Excluding cores.
%     \item PSys: Includes the consumption of the system-on-chip (SoC) which along with the processor usually includes a GPU, memory, power management circuits and USB controller. Only available on a smaller subset of models.
% \end{itemize}

\input{tabels/RAPL_Domain.tex}

The energy counters in RAPL can be accessed by utilizing model-specific registers (MSRs). By default, these counters are updated every 1 ms. These MSRs can be accessed on Linux and supplies an interface for doing read operations directly on the CPU.\cite{linux_manual_msr}. There are also alternatives to using the MSRs. The Power Capping Framework allows the user to access RAPL by using sysfs, which is a pseudo file system in the Linux kernel\cite{PowerCappingFramework,RAPL_in_action}. Furthermore, \texttt{perf} or \texttt{perf\_events} are Linux commands available in the Linux kernel which allows to access performance counters.\cite{Perf_events,RAPL_in_action}\newline

Another option is the Performance Application Programming Interface (PAPI) library, which is a tool that can be used to measure the performance and provide an interface so the measurement in near real time\cite{PAPI}.
Mozilla also has a tool which can print all the available RAPL power estimates\cite{FireFox}\nytafsnit

%% Der er ogsp jRAPL, men det virker kun med java

%% mozilla rapl

In the litterature, different limitations are mentioned with respect to RAPL. This includes for example poor driver support as drivers are only available for the Linux kernel and therefore not for Windows.\cite{RAPL_in_action} Work has also been done on how to exploit the information given by the RAPL interface, as it is argued that the security aspect has not been considered when developing RAPL\cite[]{Zhang2021}. This is regarding how information can be exploited to mount attacks. This has to do with how the fine-grained power consumption of different components of the system can be accessed and read. Using this information, one study used a RAPL-based website fingerprint technique to identify visited webpages with accuracies up to $99$\% on Chrome and $81$\% in Tor\cite[]{Zhang2021} and in the work by Mantel et al.\cite[]{Mantel2018} they can distinguish between different Rivest-Shamir-Adleman (RSA) secret keys only using energy measurements with an accuracy of 99\%. To fix this issue, Intel recommends only giving read access to trusted users and enabling Intel Software Guard Extensions (SGX) or using a specific architectural MSR feature. This means the energy information report will be modified, where random energy noise is included in the calculation which creates a small delta between the reported power consumption and actual power consumption. It is however also possible not to enable this, and gain the most accurate readings.\cite[]{intel_rapl_security}

%% We can go into more depth if needed "RAPL in Action: Experiences in using RAPL for Power Measurement"