\subsection{DUTs}\label[subsec]{subsec:DUTs}

Following the introduction to what kind of DUTs are required for our work in \cref{subsec:setup}, this section will introduce the DUTs able to meet the requirements. Before going into depth with each DUT, some overall comments can be made about them. One requirement for the DUTs is regarding the OSs, here the versions of both Linux and Windows should be the same across all DUTs, to make the results more comparable. The specific versions were the most recent update when the experiments were executed in November 2022. Each DUT was in addition to this running on a fresh install of each OS, to limit unnecessary background processes. Following this, the three DUTs can be introduced.

\paragraph{Surface Book:} The first DUT was the Surface Book, first released in October 2015, where the specifications can be seen in \cref{tab:surfaceBook}. This DUT was the most difficult one to find, as this is the one with a MAXIM chip. The reason why this DUT was difficult to find, was because the MAXIM chip is not mentioned anywhere in the documentation for this Surface Book, or any newer versions of any Surface devices. Because of this, it was a challenge to ensure the DUT had the chip. The Surface Book was chosen as a teardown was found\feetnote{https://www.ifixit.com/Teardown/Microsoft+Surface+Book+Teardown/51972}, where the chip was pointed out.

\input{tabels/SurfaceBook.tex}

\paragraph{Surface Pro 4:} The Surface Pro 4 represents the DUT with a battery, but without a MAXIM chip, and was chosen based on what was available at the University. The DUT was released in October of 2015, meaning it is from the same generation as the Surface Book, but with an upgraded CPU and more RAM, as can be seen in \cref{tab:surfacePro}.

\input{tabels/SurfacePro.tex}

\paragraph{Workstation:} The workstation represents the DUT without a battery, making it possible to measure the energy consumption through a hardware measuring instrument. This DUT was also chosen based on what was available at the University and came with a external GPU, which was removed for comparability as neither of the other DUTs had an external GPU.

\input{tabels/Komplett.tex}