\subsection{Anomalies Detection}\label[subsec]{subsec:anomalies_detection}

Anomaly detection was found to be an important tool to avoid corrupted results. For this, the DBSCAN algorithm was found in \cref{subsec:anomalies} to be the algorithm of choice to find anomalies in the data.

\paragraph*{}
An example of a test case measurement for the workstation is shown in \cref{fig:anomaly_detection_example}. The example is of the test case Fasta measured by LHM, but outliers have been detected and removed for all test case measurements.

\paragraph*{}
The algorithm DBSCAN used to find outliers is described in the work by Ester et al.\cite{ester1996density}. To use this algorithm, the value of two parameters needs to be decided, this being \texttt{Eps} and \texttt{MinPts}. to do this, a \texttt{k-dist} function is defined, where $k$ represents the distance from a point to its $k$'th neighbor. This function is applied to all data points, where each data point represents a measurement. The output from applying the \texttt{k-dist} to all measurements is plotted in descending order. This is called the sorted k-dist graph and can be seen in \cref{fig:4-dist}. The next step is to choose a threshold point, which is the last point in the first "valley" on the graph. All points with a higher k-dist value will then be considered to be noise. The \texttt{MinPts} will in this case be set to \texttt{k}, and \texttt{Eps} will be the $y$ value of \texttt{k-dist(p)}. When finding this "valley", it is noted in the work by Ester et al.\cite{ester1996density} to be very difficult to find the "valley" automatically, but it is however easy for a user to see it. Because of this, the process of finding the "valley" is done manually for all cases. In this example, the first valley is marked in \cref{fig:4-dist} with a dotted line, where the \texttt{Eps} parameter is set to $0.00105$. Based on this, the outliers can be found and removed. This is illustrated in \cref{fig:outliers}, where the outliers are marked in red.

\input{tabels/experiment_results/outliers/outliers_graph.tex}


