\section{Experiment \#2}\label{sec:experiment_two}

During Experiment \#1 in \cref{sec:experiment_one}, a few observations made seemed to different compared to expectations. This is first of all regarding that Linux had a lower energy consumption than Windows when comparing the clamp measurements, and second of all that the energy consumption of the idle test case is lower compared to the expected energy consumption of the different DUT's covered in \cref{subsec:expec_energy_consumption}. Because of this, a second experiment was introduced to look into this. One difference between the first and second experiment is how many test case measurements were made. In the first experiment $120$ was made, but this was found in \cref{subsec:CockUse} to be too many. In this experiments only $20$ measurements were made. 

\paragraph*{}
This experiment will aim to uncover why the idle test case had a lower energy consumption than expected. The expectation is that the low energy consumption measured on the idle test case also impacts the dynamic energy consumption on the different OSs, resulting in a higher energy consumption for Windows. A solution will thus increase the idle test case energy consumption, and decrease the dynamic energy consumption for all test cases, where they will be decreased more on Windows. 

\paragraph*{}
An example of the idle test case energy consumption being lower than expected can be observed in \cref{fig:TestCaseIdle_Cores_comparison_energy_without_outliers_PowerKomplett_avg_watts}. Here the idle test cases median energy consumption is reported by Intel Power Gadget to be $2.24W$ on the workstation, where the expectations were between $10W$ and $65W$. Because of this, some further investigation into the results was conducted. In terms of why the measurements were so low, a few things could have caused it, which will be covered now.

\input{tabels/experiment_results/exp_one/comparison/PowerKomplett/energy/without_outliers/Cores/TestCaseIdle.tex}

\input{sections/experiments/2-experiment/idle_experiments.tex}